


<head>
  <meta charset="utf-8" />
  <title>TB Data Quality</title>
  <link rel="stylesheet" type="text/css" href="../css/jquery-ui.css" />
  <script src="http://code.jquery.com/jquery-1.9.1.js"></script>
  <script src="http://code.jquery.com/ui/1.10.3/jquery-ui.js"></script>
  <link rel="stylesheet" type="text/css" href="../css/tb_report.css" />
  <script>
  $(function() {
    $( "#tabs" ).tabs();
  });
  </script>
</head>


```{r setup, echo = FALSE, message = FALSE, warning = FALSE}

# Strings ain't factors
options(stringsAsFactors = FALSE)

# Load the required libraries
library(knitr)
library(mpmisc)
library(tbdbaid)
library(RODBC)
library(plyr)


# Set default chunk options
opts_chunk$set(echo = FALSE,
               results = 'asis',
               message = FALSE,
               warning = FALSE,
               error = TRUE)



# Set up the database connection
# One for the quarterly report functions, which take the odbc connection as a string
if(interactive()) { 
    dbconnect <- "tbdbplus64"
} else {
    dbconnect <- "tbdbplus32"
}

# Another for queries that will expect an actual ODBC connection object
plus <- connect_to_tbdbplus()
    



```



# TB Clinic Data Quality Report
Updated at `r paste(Sys.time())`



<div id="tabs">
  <ul>
    <li><a href="#txplans">Treatment</a></li>
    <li><a href="#ptclass">Patient Classification</a></li>
    <li><a href="#diagnostics">Diagnostics</a></li>
    <li><a href="#encounters">Encounters</a></li>
    <li><a href="#locating">Locating Info</a></li>
  </ul>
    

  <div id="txplans">
  
## Treatment Plan/Classification Mismatch
  ```{r plan_class_mismatch}
  
  # Pull open plans
  plantypes <- sqlQuery(plus, "
                    
      SELECT t.person_id, c.current_class,  t.treat_plan_type, 
             t.treat_plan_date, t.case_manager, t.plan_status
      FROM Tx_Plan_View t LEFT OUTER JOIN Case_Info_View c
      ON t.person_id = c.person_id
      WHERE t.plan_status = 'Open'
          AND (case_manager_affiliation = 'Denver Metro TB Clinic'
               OR author_affiliation = 'Denver Metro TB Clinic')
                        
  ")
  
  # Flag discordant class/plans
  plantypes$discordant <- FALSE
  
  # Any treatment plan for the uninfected
  plantypes$discordant[plantypes$current_class %in% c("Class 0", "Class 1") &
                       plantypes$treat_plan_type %in% c("LTBI", "Active")] <- TRUE
  
  # Active plans for LTBI+
  plantypes$discordant[plantypes$current_class %in% "Class 2" &
                       plantypes$treat_plan_type %in% "Active"] <- TRUE
  
  # LTBI and Window plans for active cases and suspects
  plantypes$discordant[plantypes$current_class %in% c("Class 3", "Class 5") &
                       plantypes$treat_plan_type %in% c("LTBI", "Window")] <- TRUE
  
  
  #count(plantypes, c("current_class", "treat_plan_type", "discordant"))
  
  
  discordant <- subset(plantypes,
                       subset = discordant,
                       select = c("person_id", "current_class", "treat_plan_type", 
                                  "treat_plan_date", "case_manager", "plan_status")
  )
  
  
  dfprintif(arrange(discordant, current_class, treat_plan_type),
            norowmsg = "All classifications and plans seem to match.")
  
  
  
  ```
  
  
## Patients with 2 or More Open Treatment Plans
  ```{r multiplan}
  
  # Query the open plans by person_id
  open_plans <- sqlQuery(plus, "
                        
      SELECT person_id, treat_plan, treat_plan_date, plan_status
      FROM Tx_Plan_View
      WHERE plan_status = 'Open'
          AND (case_manager_affiliation = 'Denver Metro TB Clinic'
               OR author_affiliation = 'Denver Metro TB Clinic')
                        
  ")
  
  # Identify any person with multiple plans
  multiplan_ids <- open_plans$person_id[duplicated(open_plans$person_id)]
  multiplans <- subset(open_plans, person_id %in% multiplan_ids)
  
  dfprintif(arrange(multiplans, person_id, treat_plan_date),
            norowmsg = "No patients have more than one open plan.")
  
  
  ```
  
  
## Treatment Plans Open Longer Than Expected
  ```{r plans_open_longer}
  
  # Query the treatment plans
  # Exclude plans prior to 2008
  long_plans <- sqlQuery(plus, "
                    
      SELECT person_id, case_manager, treat_plan_date,
             treat_plan_type, ltbi_drug,
             latest_tx, plan_status, reason_stopped
      FROM Tx_Plan_View
      WHERE (case_manager_affiliation = 'Denver Metro TB Clinic'
             OR author_affiliation = 'Denver Metro TB Clinic')
          AND plan_status = 'Open'
          AND treat_plan_date > #2008-01-01#
                    
  ")
  
  # Convert treat_plan_date to Date
  long_plans$treat_plan_date <- as.Date(long_plans$treat_plan_date)
  
  # Calculate how long each plan has been open
  long_plans$days_open <- Sys.Date() - long_plans$treat_plan_date
  
  # Flag those that have been open too long
  # Rifampin - more than 4 months
  # INH - more than 9 months
  # INH/Rifapentine - more than 12 weeks
  # Active - more than 12 months
  long_plans$open_too_long <- FALSE
  long_plans$open_too_long[long_plans$ltbi_drug %in% "RIF" & 
                               long_plans$days_open > 124] <- TRUE
  
  long_plans$open_too_long[long_plans$ltbi_drug %in% "INH" & 
                               long_plans$days_open > 279] <- TRUE
  
  long_plans$open_too_long[long_plans$ltbi_drug %in% "INH/Rifapentine" & 
                               long_plans$days_open > 84] <- TRUE
  
  long_plans$open_too_long[long_plans$treat_plan_type %in% "Active" & 
                               long_plans$days_open > 365] <- TRUE
  
  open_too_long <- subset(long_plans,
                          subset = open_too_long,
                          select = c("person_id", "case_manager",
                                     "treat_plan_type", "ltbi_drug",
                                     "treat_plan_date", "latest_tx",
                                     "plan_status", "reason_stopped", "days_open"))
  
  
  
  dfprintif(arrange(open_too_long, case_manager, treat_plan_type, ltbi_drug, desc(days_open)),
            norowmsg = "No plans have been open longer than expected.")
  
  
  
  ```
  
  
## Treatment Plans Closed Without Reason or End Date
  ```{r closed_without}
  
  
  # Query the treatment plans
  # Every plan should have a reason stopped. They should all have a treatment ending date,
  # too, but to keep this list to a reasonable length I'll only pull completed plans that are
  # missing end dates.
  closed_without <- sqlQuery(plus, "
                    
      SELECT person_id, case_manager, treat_plan_date,
             treat_plan, plan_status, reason_stopped,
             treat_plan_end
      FROM Tx_Plan_View
      WHERE (case_manager_affiliation = 'Denver Metro TB Clinic'
             OR author_affiliation = 'Denver Metro TB Clinic')
          AND plan_status = 'Closed'
          AND (reason_stopped = 'Select One'
               OR (reason_stopped = 'Course Completed'
                   AND treat_plan_end Is Null
               )
          )
      ORDER BY case_manager, treat_plan_date
                    
  ")
  
  
  dfprintif(closed_without,
            norowmsg = "All closed treatment plans have end dates and reasons stopped.")
  
  
  ```
  
  
## Open Treatment Plans with Reason Stopped or End Date
  ```{r open_with}
  
  
  # Query the treatment plans
  # Every plan with a reason stopped or an end date should be closed
  open_with <- sqlQuery(plus, "
                    
      SELECT person_id, case_manager, treat_plan_date,
             treat_plan, plan_status, reason_stopped,
             treat_plan_end
      FROM Tx_Plan_View
      WHERE (case_manager_affiliation = 'Denver Metro TB Clinic'
               OR author_affiliation = 'Denver Metro TB Clinic')
          AND plan_status = 'Open'
          AND (reason_stopped <> 'Select One'
               OR treat_plan_end Is Not Null)
      ORDER BY case_manager, treat_plan_date
                    
  ")
  
  
  dfprintif(arrange(open_with, reason_stopped),
            norowmsg = "No open plans have end dates or reasons stopped.")
  
  
  ```
  
  
  
  
  </div>
  
  
  
  
  
  <div id="ptclass">
  
## Suspects Open for More Than 90 Days
  ```{r overdue_suspects}
  
  # Query the Case Info records of suspects associated with our clinic
  # Ignore any with a status set before 2007
  suspects <- sqlQuery(plus, "
  
      SELECT person_id,
             case_status,
             current_status, 
             current_status_date,
               DATE() - current_status_date AS days_since_status,
  		       case_manager
      FROM Case_Info_View
      WHERE current_status = '(Class 5 ) TB Suspect'
          AND case_manager Is Not Null 
          AND agency IN ('Denver Public Health - Metro TB Clinic', 'Select One')
      ORDER BY case_manager, current_status_date
                        
  ")
  
  # Convert that dt to a date
  suspects$current_status_date <- as.Date(suspects$current_status_date)
  
  
  # Identify suspects to close
  suspects$to_close <- FALSE
  
  # Suspects prior to 2007 can stay suspects, but should be closed
  suspects$to_close[suspects$current_status_date < as.Date("2007-01-01") &
                    suspects$case_status %in% "Open"] <- TRUE
  
  # Suspects with no status date should also be closed, if possible
  suspects$to_close[is.na(suspects$current_status_date) &
                    suspects$case_status %in% "Open"] <- TRUE
  
  # Finally, for cases after 2007, anyone suspected over 90 days should be reclassified
  suspects$to_close[suspects$current_status_date >= as.Date("2007-01-01") &
                    suspects$days_since_status > 90] <- TRUE
  
  
  
  # Subset to suspects to close, and drop the to_close column
  suspects_to_close <- suspects[suspects$to_close, !names(suspects) %in% "to_close"]
  
  
  dfprintif(suspects_to_close,
            norowmsg = "No suspects have been open more than 90 days.")
  
  ```
  
  
  
  
  </div>
  
  
  
  <div id="diagnostics">
  
## TSTs with Missing Results
  ```{r tsts_missing_results}
  
  # Query TSTs either placed or read by our staff but without results
  # Disregard tests placed before 2009
  tsts_no_result <- sqlQuery(plus, "
                   
      SELECT person_id, date_given, date_read, tst_read_by, result
      FROM TST_View
      WHERE reader_affiliation = 'Denver Metro TB Clinic'
          AND result = 'Select One'
          AND date_given >= #2009-01-01#
      ORDER BY tst_read_by, date_given
                   
  ")
  
  dfprintif(subset(tsts_no_result, as.Date(date_given) < (Sys.Date() - 3)),
            norowmsg = "No TSTs are missing results at this time.")
  
  
  ```
  
  
## QFTs with Missing Results
  ```{r qfts_missing_results}
  
  # Query the DPH QFTs
  qfts_no_result <- sqlQuery(plus, "
                   
      SELECT q.person_id, p.local_id AS mrn,
             q.lab, q.collection_date, q.result
      FROM QFT_View q LEFT OUTER JOIN Person p
      ON q.person_id = p.idnumber
      WHERE q.lab = 'Denver Public Health'
          AND q.result = 'Select One'
                   
  ")
  
  # Convert the collection date
  qfts_no_result$date_collected <- as.Date(qfts_no_result$collection_date, 
                                           format = "%m/%d/%Y")
  
  
  qfts_no_result_print <- subset(qfts_no_result,
      subset = date_collected < (Sys.Date() - 2),
      select = !names(qfts_no_result) %in% "collection_date"
  )
  
  dfprintif(arrange(qfts_no_result_print, date_collected),
            norowmsg = "No QFTs are missing results at this time.")
  
  
  ```
  
  
  
  </div>
  
  
  
  <div id="encounters">
  
  
## Clinical Encounters with No Staff Responsible
  ```{r encounters_nostaff}
  
  # Query encounters with no staff responsible (clinical only - don't worry about admin)
  no_staff <- sqlQuery(plus, "
                       
      SELECT person_id, eval_date, eval_category, updated_by
      FROM Eval_View
      WHERE staff_responsible Is Null
          AND eval_category = 'Clinical'
          AND updated_by IN (
              SELECT staff_userid
              FROM Def_staff
              WHERE affiliation = 'Denver Metro TB Clinic'
              )
      ORDER BY updated_by, eval_date
                       
  ")
  
  dfprintif(no_staff,
            norowmsg = "All encounters have a staff person recorded.")
  
  ```
  
  
  
  
  
  
## Visits with No Location
  ```{r no_location}
  
  # Query encounters with visit_location = 0 ("Select One").
  # Only pull face-to-face encounters - that's eval_category = 'Clinical'
  # Ignore the NAs - those are imported records that predate TBdb.
  enc <- sqlQuery(plus, "
                  
      SELECT person_id, eval_date, staff_responsible
      FROM Eval_View
      WHERE visit_location = 'Select One'
          AND eval_category = 'Clinical'
          AND eval_date >= #2011-01-01#
          AND staff_affiliation = 'Denver Metro TB Clinic'
      ORDER BY staff_responsible, eval_date
                  
  ")
  
  dfprintif(enc,
            norowmsg = "All encounters have a location recorded.")
  
  
  ```
  
  
  </div>
  
  
  <div id="locating">
  
  
## Addresses with No County
  ```{r no_county}
  
  # Query addresses with no county indicated
  # Ignore the really old ones
  # Colorado cities only
  no_county <- sqlQuery(plus, "
                        
      SELECT a.person_id, a.address, a.city, d.county,
             a.updated_by, a.updated_date
      FROM Addresses a LEFT OUTER JOIN Def_county d
      ON a.county = d.county_of_residence
      WHERE (d.county = 'Unknown'
             OR d.county Is Null)
          AND a.updated_date > #2010-01-01#
          AND a.state = 'CO'
          AND a.updated_by IN (
              SELECT staff_userid
              FROM Def_staff
              WHERE affiliation = 'Denver Metro TB Clinic'
              )
      ORDER BY a.updated_by, a.updated_date
  
  ")
  
  dfprintif(no_county,
            norowmsg = "All addresses have a county recorded.")
  
  ```
  
  </div>


</div>








```{r cleanup}

# Close the database connection
odbcClose(plus)


```



