


<head>
  <meta charset="utf-8" />
  <title>TB Data Quality</title>
  <link rel="stylesheet" type="text/css" href="../css/jquery-ui.css" />
  <script src="http://code.jquery.com/jquery-1.9.1.js"></script>
  <script src="http://code.jquery.com/ui/1.10.3/jquery-ui.js"></script>
  <link rel="stylesheet" type="text/css" href="../css/tb_report.css" />
  <script>
  $(function() {
    $( "#tabs" ).tabs();
  });
  </script>
</head>


```{r setup, echo = FALSE, message = FALSE, warning = FALSE}

# Strings ain't factors
options(stringsAsFactors = FALSE)

# Load the required libraries
library(knitr)
library(mpmisc)
library(tbdbaid)
library(RODBC)
library(plyr)


# Set default chunk options
opts_chunk$set(echo = FALSE,
               results = 'asis',
               message = FALSE,
               warning = FALSE,
               error = TRUE)



# Set up the database connection
# One for the quarterly report functions, which take the odbc connection as a string
if(interactive()) { 
    dbconnect <- "tbdbplus64"
} else {
    dbconnect <- "tbdbplus32"
}

# Another for queries that will expect an actual ODBC connection object
plus <- connect_to_tbdbplus()




```



# TB Clinic Data Quality Report
Updated at `r paste(Sys.time())`



<div id="tabs">
  <ul>
    <li><a href="#txplans">Treatment</a></li>
    <li><a href="#ptclass">Patient Classification</a></li>
    <li><a href="#diagnostics">Diagnostics</a></li>
    <li><a href="#encounters">Encounters</a></li>
    <li><a href="#locating">Locating Info</a></li>
    <li><a href="#demographics">Demographics</a></li>
  </ul>


  <div id="txplans">

## Treatment Plan/Classification Mismatch
```{r plan_class_mismatch}

  # Pull open plans
  plantypes <- sqlQuery(plus, "

      SELECT t.person_id, c.current_class,  t.treat_plan_type, 
             t.treat_plan_date, t.case_manager, t.plan_status
      FROM Tx_Plan_View t LEFT OUTER JOIN Case_Info_View c
      ON t.person_id = c.person_id
      WHERE t.plan_status = 'Open'
          AND (case_manager_affiliation = 'Denver Metro TB Clinic'
               OR author_affiliation = 'Denver Metro TB Clinic')

  ")

  # Flag discordant class/plans
  plantypes$discordant <- FALSE

  # Any treatment plan for the uninfected
  plantypes$discordant[plantypes$current_class %in% c("Class 0", "Class 1") &
                       plantypes$treat_plan_type %in% c("LTBI", "Active")] <- TRUE

  # Active plans for LTBI+
  plantypes$discordant[plantypes$current_class %in% "Class 2" &
                       plantypes$treat_plan_type %in% "Active"] <- TRUE

  # LTBI and Window plans for active cases and suspects
  plantypes$discordant[plantypes$current_class %in% c("Class 3", "Class 5") &
                       plantypes$treat_plan_type %in% c("LTBI", "Window")] <- TRUE


  #count(plantypes, c("current_class", "treat_plan_type", "discordant"))


  discordant <- subset(plantypes,
                       subset = discordant,
                       select = c("person_id", "current_class", "treat_plan_type", 
                                  "treat_plan_date", "case_manager", "plan_status")
  )


  dfprintif(arrange(discordant, current_class, treat_plan_type),
            norowmsg = "All classifications and plans seem to match.")



```


## Patients with 2 or More Open Treatment Plans
```{r multiplan}

  # Query the open plans by person_id
  open_plans <- sqlQuery(plus, "

      SELECT person_id, treat_plan, treat_plan_date, plan_status
      FROM Tx_Plan_View
      WHERE plan_status = 'Open'
          AND (case_manager_affiliation = 'Denver Metro TB Clinic'
               OR author_affiliation = 'Denver Metro TB Clinic')

  ")

  # Identify any person with multiple plans
  multiplan_ids <- open_plans$person_id[duplicated(open_plans$person_id)]
  multiplans <- subset(open_plans, person_id %in% multiplan_ids)

  dfprintif(arrange(multiplans, person_id, treat_plan_date),
            norowmsg = "No patients have more than one open plan.")


```



## Treatment Plans Closed Without Reason or End Date
```{r closed_without}


  # Query the treatment plans
  # Every plan should have a reason stopped. They should all have a treatment ending date,
  # too, but to keep this list to a reasonable length I'll only pull completed plans that are
  # missing end dates.
  closed_without <- sqlQuery(plus, "

      SELECT person_id, case_manager, treat_plan_date,
             treat_plan, plan_status, reason_stopped,
             treat_plan_end
      FROM Tx_Plan_View
      WHERE (case_manager_affiliation = 'Denver Metro TB Clinic'
             OR author_affiliation = 'Denver Metro TB Clinic')
          AND plan_status = 'Closed'
          AND (reason_stopped = 'Select One'
               OR (reason_stopped = 'Course Completed'
                   AND treat_plan_end Is Null
               )
          )
      ORDER BY case_manager, treat_plan_date

  ")


  dfprintif(closed_without,
            norowmsg = "All closed treatment plans have end dates and reasons stopped.")


```


## Open Treatment Plans with Reason Stopped or End Date
```{r open_with}


  # Query the treatment plans
  # Every plan with a reason stopped or an end date should be closed
  open_with <- sqlQuery(plus, "

      SELECT person_id, case_manager, treat_plan_date,
             treat_plan, plan_status, reason_stopped,
             treat_plan_end
      FROM Tx_Plan_View
      WHERE (case_manager_affiliation = 'Denver Metro TB Clinic'
               OR author_affiliation = 'Denver Metro TB Clinic')
          AND plan_status = 'Open'
          AND (reason_stopped <> 'Select One'
               OR treat_plan_end Is Not Null)
      ORDER BY case_manager, treat_plan_date

  ")


  dfprintif(arrange(open_with, reason_stopped),
            norowmsg = "No open plans have end dates or reasons stopped.")


```





## Treatment Plans Open Longer Than Expected
```{r plans_open_longer}

  # Query the treatment plans
  # Exclude plans prior to 2008
  long_plans <- sqlQuery(plus, "

      SELECT person_id, case_manager, treat_plan_date,
             treat_plan_type, ltbi_drug,
             latest_tx, plan_status, reason_stopped
      FROM Tx_Plan_View
      WHERE (case_manager_affiliation = 'Denver Metro TB Clinic'
             OR author_affiliation = 'Denver Metro TB Clinic')
          AND plan_status = 'Open'
          AND treat_plan_date > #2008-01-01#

  ")

  # Convert treat_plan_date to Date
  long_plans$treat_plan_date <- as.Date(long_plans$treat_plan_date)

  # Calculate how long each plan has been open
  long_plans$days_open <- Sys.Date() - long_plans$treat_plan_date

  # Flag those that have been open too long
  # Rifampin - more than 4 months
  # INH - more than 9 months
  # INH/Rifapentine - more than 12 weeks
  # Active - more than 12 months
  long_plans$open_too_long <- FALSE
  long_plans$open_too_long[long_plans$ltbi_drug %in% "RIF" & 
                               long_plans$days_open > 124] <- TRUE

  long_plans$open_too_long[long_plans$ltbi_drug %in% "INH" & 
                               long_plans$days_open > 279] <- TRUE

  long_plans$open_too_long[long_plans$ltbi_drug %in% "INH/Rifapentine" & 
                               long_plans$days_open > 84] <- TRUE

  long_plans$open_too_long[long_plans$treat_plan_type %in% "Active" & 
                               long_plans$days_open > 365] <- TRUE

  open_too_long <- subset(long_plans,
                          subset = open_too_long,
                          select = c("person_id", "case_manager",
                                     "treat_plan_type", "ltbi_drug",
                                     "treat_plan_date", "latest_tx",
                                     "plan_status", "reason_stopped", "days_open"))



  dfprintif(arrange(open_too_long, case_manager, treat_plan_type, ltbi_drug, desc(days_open)),
            norowmsg = "No plans have been open longer than expected.")



```




## 'Window' Treatment Plans Lasting More Than 14 Weeks

```{r long_window}


# Query the treatment plans
# Exclude plans started before 2008
long_window <- sqlQuery(plus, "

    SELECT person_id, case_manager, treat_plan, reason_stopped,
           treat_plan_date, latest_tx
    FROM Tx_Plan_View
    WHERE (case_manager_affiliation = 'Denver Metro TB Clinic'
           OR author_affiliation = 'Denver Metro TB Clinic')
        AND reason_stopped = 'Window Tx Complete'
        AND treat_plan_date > #2008-01-01#

")

# Convert some dates to Date
long_window$treat_plan_date <- as.Date(long_window$treat_plan_date)
long_window$latest_tx <- as.Date(long_window$latest_tx)


# Calculate length of treatment
long_window$length_of_tx <- long_window$latest_tx - long_window$treat_plan_date


# Print any longer-than-expected plan
dfprintif(subset(long_window, length_of_tx > (7 * 14)),
          norowmsg = "All window treatment plans were completed within twelve weeks.")


```






</div>





  <div id="ptclass">

## Patients Classified as Suspects for More Than 90 Days

```{r overdue_suspects}

# Query the Case Info records of suspects associated with our clinic
# Ignore any with a status set before 2007
suspects <- sqlQuery(plus, "

    SELECT person_id,
           case_status,
           current_status, 
           current_status_date,
           DATE() - current_status_date AS days_since_status,
  		   case_manager
    FROM Case_Info_View
    WHERE current_status = '(Class 5 ) TB Suspect'
        AND case_manager Is Not Null 
        AND agency IN ('Denver Public Health - Metro TB Clinic', 'Select One')
    ORDER BY case_manager, current_status_date

")

# Convert that dt to a date
suspects$current_status_date <- as.Date(suspects$current_status_date)


# Identify suspects to close
suspects$to_close <- FALSE

# Suspects prior to 2007 can stay suspects, but should be closed
suspects$to_close[suspects$current_status_date < as.Date("2007-01-01") &
                  suspects$case_status %in% "Open"] <- TRUE

# Suspects with no status date should also be closed, if possible
suspects$to_close[is.na(suspects$current_status_date) &
                  suspects$case_status %in% "Open"] <- TRUE

# Finally, for cases after 2007, anyone suspected over 90 days should be reclassified
suspects$to_close[suspects$current_status_date >= as.Date("2007-01-01") &
                  suspects$days_since_status > 90] <- TRUE



# Subset to suspects to close, and drop the to_close column
suspects_to_close <- suspects[suspects$to_close, !names(suspects) %in% "to_close"]


dfprintif(suspects_to_close,
          norowmsg = "No suspects have been open more than 90 days.")


```


## Patients with Pending Status for More Than 90 Days

```{r pending}

pending <- sqlQuery(plus, "

    SELECT person_id,
           current_status, 
           case_status,
           current_status_date,
           DATE() - current_status_date AS days_since_status,
      	   case_manager
    FROM Case_Info_View
    WHERE current_status = 'Pending'
        AND case_manager Is Not Null 
        AND agency IN ('Denver Public Health - Metro TB Clinic', 'Select One')
        AND current_status_date > #2007-01-01#
    ORDER BY case_manager, current_status_date

 ")




# Convert that dt to a date
pending$current_status_date <- as.Date(pending$current_status_date)


# Identify pending to close
pending$to_close <- FALSE

# pending prior to 2007 can stay pending, but should be closed
pending$to_close[pending$current_status_date < as.Date("2007-01-01") &
                  pending$case_status %in% "Open"] <- TRUE

# pending with no status date should also be closed, if possible
pending$to_close[is.na(pending$current_status_date) &
                  pending$case_status %in% "Open"] <- TRUE

# Finally, for cases after 2007, anyone pending over 90 days should be reclassified
pending$to_close[pending$current_status_date >= as.Date("2007-01-01") &
                  pending$days_since_status > 90] <- TRUE



# Subset to pending to close, and drop the to_close column
pending_to_close <- pending[pending$to_close, !names(pending) %in% "to_close"]


dfprintif(pending_to_close,
          norowmsg = "No pending have been open more than 90 days.")


```


## Patients Closed with No Current Classification

```{r noclass}


# I'm excluding open cases because there are nearly 6000 - but do they need to be
# fixed, too?
noclass <- sqlQuery(plus, "

    SELECT person_id, current_class, case_status
    FROM Case_Info_View
    WHERE current_class IS NULL
        AND agency = 'Denver Public Health - Metro TB Clinic'
        AND case_status = 'Closed'

")


dfprintif(noclass,
          norowmsg = "All closed patients have a classification.")


```




</div>



<div id="diagnostics">

## TSTs with Missing Results
```{r tsts_missing_results}

  # Query TSTs either placed or read by our staff but without results
  # Disregard tests placed before 2009
  tsts_no_result <- sqlQuery(plus, "

      SELECT person_id, date_given, date_read, tst_read_by, result
      FROM TST_View
      WHERE reader_affiliation = 'Denver Metro TB Clinic'
          AND result = 'Select One'
          AND date_given >= #2008-01-01#
      ORDER BY tst_read_by, date_given

  ")

  dfprintif(subset(tsts_no_result, as.Date(date_given) < (Sys.Date() - 3)),
            norowmsg = "No TSTs are missing results at this time.")


```


## QFTs with Missing Results
```{r qfts_missing_results}

  # Query the DPH QFTs
  qfts_no_result <- sqlQuery(plus, "

      SELECT q.person_id, p.local_id AS mrn,
             q.lab, q.collection_date, q.result, q.last_updated_by
      FROM QFT_View q LEFT OUTER JOIN Person p
      ON q.person_id = p.idnumber
      WHERE q.lab = 'Denver Public Health'
          AND q.result = 'Select One'

  ")

  # Convert the collection date
  qfts_no_result$date_collected <- as.Date(qfts_no_result$collection_date, 
                                           format = "%m/%d/%Y")


  qfts_no_result_print <- subset(qfts_no_result,
      subset = date_collected < (Sys.Date() - 2),
      select = c("person_id", "mrn", "date_collected",
                 "lab", "result", "last_updated_by")
  )

  dfprintif(arrange(qfts_no_result_print, date_collected),
            norowmsg = "No QFTs are missing results at this time.")


```


## QFTs with Mismatched Results

These QFTs have different results in TBdb than in the corresponding Data Warehouse record - check LCR.

```{r qfts_mismatched}

  # Query the DPH QFTs from TBdb
  # Patients whose results haven't been entered into TBdb should be covered
  # by the above report, so I'm excluding them here
  qfts_tbdb <- sqlQuery(plus, "

      SELECT q.quantiferonid,
             q.person_id, p.local_id AS mrn,
             q.lab, q.collection_date, q.result, q.last_updated_by
      FROM QFT_View q LEFT OUTER JOIN Person p
      ON q.person_id = p.idnumber
      WHERE q.lab = 'Denver Public Health'
          AND q.result <> 'Select One'

  ")


  # Query the QFTs from the DH Data Warehouse
  qfts_dhdw <- subset(
      query_dhdw_qfts(start_date = as.Date("2010-01-01"),
                      stop_date = Sys.Date() - 14),
      select = c("mrn", "qft_dt", "result")
  )


  # Convert the collection dates
  qfts_tbdb$date_collected <- as.Date(qfts_tbdb$collection_date, 
                                      format = "%m/%d/%Y")

  qfts_dhdw$date_collected <- as.Date(qfts_dhdw$qft_dt,
                                      tz = "MST")

  # Strip anything longer than 7 characters from the TBdb MRNs
  qfts_tbdb$mrn <- substr(qfts_tbdb$mrn, 1, 7)

  # Restore leading zeroes to MRNs
  qfts_tbdb$mrn <- formatC(qfts_tbdb$mrn, width = 7, format = "d", flag = "0")
  qfts_dhdw$mrn <- formatC(qfts_dhdw$mrn, width = 7, format = "d", flag = "0")




  # Flag each record's origin
  qfts_tbdb$origin <- "TBdb"
  qfts_dhdw$origin <- "DHDW"


  # Merge the DHDW QFTs onto those from TBdb
  # (Ideally this would be a full outer join, but I don't have a way to
  # select just DPH QFTs from the DHDW yet)
  qfts_compare <- merge(x = subset(qfts_tbdb, 
                                   date_collected > as.Date("2010-01-01") &
                                   date_collected < (Sys.Date() - 14)),
                        y = qfts_dhdw,
                        by = c("mrn", "date_collected"),
                        all.x = TRUE,
                        suffixes = c(".tbdb", ".dhdw")
  )

  # Subset to discordant tests
  qfts_discordant <- subset(qfts_compare,
                            subset = result.tbdb != result.dhdw,
                            select = c("mrn", "person_id", "date_collected",
                                       "result.tbdb", "result.dhdw",
                                       "last_updated_by")
  )


# Pretty names
names(qfts_discordant) <- c("MRN", "TBdb ID", "Date Collected",
                                  "Result in TBdb", "Result in DHDW",
                                  "Last Updated By")

# Print it
dfprintif(arrange(qfts_discordant, `Date Collected`),
          norowmsg = "All QFT results in TBdb appear to be consistent with their counterparts in the DH Data Warehouse.")


```



## QFTs Not Matched In the Data Warehouse

Possible reasons:

 - MRN is missing from TBdb,
 - MRN is different in TBdb and the Data Warehouse,
 - different dates in TBdb and LCR, 
 - QFT not actually performed by DH lab

```{r qfts_not_in_dhdw}

# Subset to QFTs with no match in the DH Data Warehouse
qfts_missing_dhdw <- subset(qfts_compare, 
                            subset = is.na(origin.dhdw) &
                                     !result.tbdb %in% c("Not Done",
                                                         "Select One") &
                                     !duplicated(quantiferonid),
                            select = c("quantiferonid",
                                       "mrn", "person_id", "date_collected",
                                       "result.tbdb", "result.dhdw",
                                       "last_updated_by")
)


# Pretty names
names(qfts_missing_dhdw) <- c("MRN", "TBdb ID", "Date Collected",
                              "Result in TBdb", "Result in DHDW",
                              "Last Updated By")

dfprintif(arrange(qfts_missing_dhdw, `Date Collected`),
          norowmsg = "All QFT results have a corresponding record in the DH Data Warehouse.")



```


## Patients with a Positive LTBI Test But No Follow-Up CXR

Excludes patients with a closed case status

```{r ltbi_no_cxr}

# Query all the TSTs and QFTs
tests <- subset(query_tests(start_date = as.Date("2008-01-01"),
                            stop_date = Sys.Date()),
                test %in% c("TST", "QFT"))


# Pull in all chest x-rays - CXRs we've ordered come in with query_tests,
# but CXRs from other places are valid here
cxrs <- sqlQuery(plus, "

    SELECT person_id, cxr_date_taken, cxr_lab
    FROM CXR_View

")


# For each patient, identify those with a positive TST or QFT
# (excluding a TST+ followed by a QFT-)
# with no subsequent CXR
screen_status <- ddply(tests, .var = "person_id", .fun = function(x) {


    # Sort the tests
    x.ord <- arrange(x[c("person_id", "test_date", "test", "result")],
                     desc(test_date))

    # Does this person have a valid positive test?
    # Get the most recent one
    latest.pos <- head(x.ord[x.ord$test %in% c("TST", "QFT") &
                             x.ord$result %in% "Positive", ], 
                       1)


    # Do they have a subsequent negative test?
    subsequent.neg <- subset(x.ord,
                             subset = test_date > latest.pos$test_date &
                                      test %in% c("TST", "QFT") &
                                      result %in% "Negative")


    # Do they have a CXR?
    subsequent.cxr <- subset(cxrs, person_id %in% x$person_id)


    # Build the results
    results <- data.frame(person_id = x$person_id[1],
                          postest = NA,
                          posdate = NA,
                          refuted = NA,
                          cxr = NA)

    if(nrow(latest.pos) > 0) {
        results$postest <- latest.pos$test
        results$posdate <- latest.pos$test_date
    }

    results$refuted <- nrow(subsequent.neg) > 0
    results$cxr <- nrow(subsequent.cxr) > 0

    results

})


# Convert dates back to Dates
screen_status$posdate <- as.Date(screen_status$posdate,
                                 origin = as.Date("1970-01-01"))


# Assume that those with closed cases were correctly closed and show
# only open cases
case_status <- sqlQuery(plus, "

    SELECT person_id, case_status
    FROM Case_Info_View

")

screen_status_open <- merge(x = screen_status,
                            y = case_status,
                            by = "person_id",
                            all.x = TRUE)



# Flag those with positive tests and no subsequent results
ltbi_no_cxr <- subset(screen_status_open,
                      subset = !is.na(postest) &
                               cxr %in% FALSE &
                               refuted %in% FALSE &
                               case_status %in% c("Pending", "Open"),
                      select = c("person_id", "postest", "posdate")
)


names(ltbi_no_cxr) <- c("TBdb ID", "Latest Positive Test", "Test Date")


dfprintif(arrange(ltbi_no_cxr, `Test Date`))



```




## Labs with No Accession Number

```{r labs_no_accession}

# Query the labs with no accession number
myco_labs <- sqlQuery(plus, "

    SELECT c.person_id, d.mrn, c.accession_number, c.collection_date
    FROM Culture c LEFT OUTER JOIN Demos_View d
    ON c.person_id = d.person_id
    WHERE originating_lab = 2
        AND (accession_number = '' OR
             accession_number IS NULL)
        AND collection_date BETWEEN #2008-01-01# AND (Date() - 7)
    ORDER BY collection_date

")


# Add an originating lab label
# The is.na() indexing is strictly to avoid an error when there
# are zero records - there must be a more elegant way around that
myco_labs$originating_lab[is.na(myco_labs$accession_number)] <- 
  "Denver Public Health"

# Convert things to character for tidier display
myco_labs$mrn <- as.character(myco_labs$mrn)
myco_labs$accession_number[is.na(myco_labs$accession_number)] <- "--"


dfprintif(myco_labs,
          norowmsg = "All lab specimens have some accession number listed.")


```


</div>



<div id="encounters">


## Clinical Encounters with No Staff Responsible
```{r encounters_nostaff}

  # Query encounters with no staff responsible (clinical only - don't worry about admin)
  no_staff <- sqlQuery(plus, "

      SELECT person_id, eval_date, eval_category, updated_by
      FROM Eval_View
      WHERE staff_responsible Is Null
          AND eval_category = 'Clinical'
          AND updated_by IN (
              SELECT staff_userid
              FROM Def_staff
              WHERE affiliation = 'Denver Metro TB Clinic'
              )
      ORDER BY updated_by, eval_date

  ")

  dfprintif(no_staff,
            norowmsg = "All encounters have a staff person recorded.")

```






## Visits with No Location
```{r no_location}

  # Query encounters with visit_location = 0 ("Select One").
  # Only pull face-to-face encounters - that's eval_category = 'Clinical'
  # Ignore the NAs - those are imported records that predate TBdb.
  enc <- sqlQuery(plus, "

      SELECT person_id, eval_date, staff_responsible
      FROM Eval_View
      WHERE visit_location = 'Select One'
          AND eval_category = 'Clinical'
          AND eval_date >= #2011-01-01#
          AND staff_affiliation = 'Denver Metro TB Clinic'
      ORDER BY staff_responsible, eval_date

  ")

  dfprintif(enc,
            norowmsg = "All encounters have a location recorded.")


```


</div>


<div id="locating">



## Addresses with No County
```{r no_county}

  # Query addresses with no county indicated
  # Ignore the really old ones
  # Colorado cities only
  no_county <- sqlQuery(plus, "

      SELECT a.person_id, a.address, a.city, d.county,
             a.updated_by, a.updated_date
      FROM Addresses a LEFT OUTER JOIN Def_county d
      ON a.county = d.county_of_residence
      WHERE (d.county = 'Unknown'
             OR d.county Is Null)
          AND a.updated_date > #2010-01-01#
          AND a.state = 'CO'
          AND a.updated_by IN (
              SELECT staff_userid
              FROM Def_staff
              WHERE affiliation = 'Denver Metro TB Clinic'
              )
      ORDER BY a.updated_by, a.updated_date

  ")

  dfprintif(no_county,
            norowmsg = "All addresses have a county recorded.")

```

</div>




<div id="demographics">


## Patients with Inconsistent Country of Birth and Immigrant Status


```{r immi_vs_birthco}

migrant <- sqlQuery(plus, "

    SELECT person_id, mrn, birthco, immi_status
    FROM Demos_View
    WHERE birthco IS NOT NULL
        AND birthco <> '<Select One>'

")


# Identify all US territories
usterr <- c("United States", 
            "Puerto Rico", 
            "United States Minor Outlying Islands",
            "Virgin Islands (U.S.)")

# Identify non-immigrant status
nonimmigrant <- c("Not Applicable (US born)", "Select One", NA)



# Flag inconsistent combinations
migrant$inconsistent <- NA

# People born in the US with any kind of immigrant status
migrant$inconsistent[migrant$birthco %in% usterr &
                     !migrant$immi_status %in% nonimmigrant] <- "US-born Immigrant"


# Not born in the US but indicated as a citizen
migrant$inconsistent[!migrant$birthco %in% usterr &
    migrant$immi_status %in% "Not Applicable (US born)"] <- "Foreign-born Native"

migrantprob <- subset(migrant,
                      subset = !is.na(inconsistent))

dfprintif(arrange(migrantprob, inconsistent, birthco, immi_status),
          norowmsg = "All patients have immigration statuses consistent with their country of birth.")


```


## Patients with No Country of Birth

```{r no_birthco}

# Query patients with no country of birth listed

no_birthco <- sqlQuery(plus, "

    SELECT person_id, mrn, birthco
    FROM Demos_View
    WHERE (birthco IS NULL OR birthco = '<Select One>')
    AND person_id > 100000
    ORDER BY mrn DESC

")


dfprintif(no_birthco,
          norowmsg = "All patients have country of birth recorded.")


```


</div>


</div>








```{r cleanup}

# Close the database connection
odbcClose(plus)


```



